---
title: "p8015_hw6_xz2981"
author: "Xinyan Zhou"
date: "12/1/2021"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

### Tidy data
Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r}
birthweight = 
  read_csv("data/birthweight.csv") %>% 
  mutate(
    babysex = case_when(
      babysex  == 1 ~ "male",
      babysex  == 2 ~ "female",
      TRUE ~ "missing"),
    frace = case_when(
      frace == 1 ~ "White",
      frace == 2 ~ "Black",
      frace == 3 ~ "Asian",
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other",
      frace == 9 ~ "Unknown",
      TRUE ~ "missing"),
     malform = case_when(
      malform == 0 ~ "absent",
      malform == 1 ~ "present",
      TRUE ~ "missing"),
     mrace = case_when(
      mrace == 1 ~ "White",
      mrace == 2 ~ "Black",
      mrace == 3 ~ "Asian",
      mrace == 4 ~ "Puerto Rican",
      TRUE ~ "missing")
    ) %>%
  mutate(babysex = factor(babysex),
         frace = factor(frace),
         malform = factor(malform),
         mrace = factor(mrace))

summary(birthweight)
```

From the results of summary, we know that there are no missing data.

### Model fit

Propose a regression model for birthweight. 

This model is based on a hypothesized structure for the factors that underlie birth weight. Based on my work experience in the Department of Obstetrics and Gynecology, I chose to include the following variables into my model: babysex, gaweeks, and wtgain.

Fit the model
```{r}
fit <- lm(bwt ~ babysex + gaweeks +  wtgain, data = birthweight)

fit %>% broom::tidy()
```

Diagnostics
```{r}
birthweight %>%
  modelr::add_residuals(fit) %>% 
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = resid, y = pred)) +
  geom_point()
```

### Compare models

Model 1
```{r}
fit_model_1 <- lm(bwt ~ blength + gaweeks, data = birthweight)

fit_model_1 %>% broom::tidy()
```

Model 2
```{r}
fit_model_2 <- lm(bwt ~ blength + gaweeks + babysex * bhead * blength, 
                  data = birthweight)

fit_model_2 %>% broom::tidy()
```

```{r}
cv_df = 
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_df =
  cv_df %>% 
  mutate(
    model_0 = map(.x = train, ~lm(bwt ~ babysex + gaweeks +  wtgain, data = .x)),
    model_1 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_2 = map(.x = train, ~lm(bwt ~ blength + gaweeks + babysex * bhead * blength,
                                  data = .x)), 
  ) %>% 
  mutate(
    rmse_model_0 = map2_dbl(.x = model_0, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model_1 = map2_dbl(.x = model_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(.x = model_2, .y = test, ~rmse(model = .x, data = .y)),
  )

cv_df %>% 
  select(.id, starts_with("rmse")) %>% 
  pivot_longer(
    rmse_model_0:rmse_model_2,
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_boxplot()
```

## Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
boot_strap_df =
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
    results_1 = map(models, broom::glance),
    results_2 = map(models, broom::tidy)
  ) %>%
  select(-strap, -models) 
```

```{r}
value_1_df <-
  boot_strap_df %>%
  unnest(results_1) %>%
  select(strap_number,r.squared)

mean(pull(value_1_df,r.squared))
quantile(pull(value_1_df,r.squared), probs = c(0.025, 0.975))  
  
value_1_df %>%
  ggplot(aes(x = r.squared)) +
  geom_density() +
  xlim(0.8,1)
```

```{r}
value_2_df <-
  boot_strap_df %>%
  unnest(results_2) %>%
  select(strap_number, term, estimate) %>%
  pivot_wider(names_from = term, values_from = estimate) %>%
  janitor::clean_names() %>%
  mutate(value_2 = log(intercept*tmin)) 

mean(pull(value_2_df,value_2))
quantile(pull(value_2_df,value_2), probs = c(0.025, 0.975))  
  
value_2_df %>%
  ggplot(aes(x = value_2)) +
  geom_density() +
  xlim(1.8,2.2)
```

